\section{Introduction}

The objective of the mini-project is to go through the control design pipeline of a three-link 2D biped, in order to design and compare different controllers, both quantitatively (metrics of success) as well as qualitatively (gaits achieved).
In particular, the report will describe the attempt at implementing three different controllers; namely a virtual constraints controller, a reinforcement learning controller, and virtual model controller using task space projection; as well as the results yielded by each controller.

\vspace{\baselineskip}

The control design pipeline consists of three steps.
The first is the modelling step, in which a model is chosen for the system of interest and implemented, along with means of visualizations.
In the case of this report, the model is the three-link 2D biped.
The second step is the control design step, in which gaits are achieved through controllers strategies.
Finally, the third step is the simulation step, which entails numerically solving the equations of motion for the model as well as collision handling, in order to have a visualization of the robot's motion.


\begin{center}
	\begin{tikzpicture}[auto]
		\node [block] (model) {Modelling};
		\node [block, below=of model] (control) {Control design};
		\node [block, below=of control] (simulation) {Simulation};

		\draw [->] (model) -- (control);
		\draw [->] (control) -- (simulation);
		\draw [->, rounded corners] (simulation) -- ++ (-2, 0) |- (control);
	\end{tikzpicture}
\end{center}

Going back and forth between control design and simulation allows the testing of different strategies, to adopt the best.
In practice, the simulation can be implemented before the controller, if it is more convenient like so, but the description of the control design pipeline makes more sense in that order, because after designing a controller, its performances are tested through simulation, before another controller might be designed and tested.

\vspace{\baselineskip}

The model for the theoretical legged robot studied here is the three-link 2D biped, which is represented on Figure~\ref{fig::model} below:

\begin{figure}[H]
	\begin{center}
		\begin{tikzpicture}
			\begin{scope}[x={8cm},y={8cm}]
				% l = 0,447213
				% alpha = 8.999999999478607 deg
				% =0.5+sqrt(0.2^2+0.4^2)*sin(pi/20)
				% =0.4+sqrt(0.2^2+0.4^2)*cos(pi/20)

				\draw[-] (0,0)--(1,0);

				\draw[-,ultra thick] (0.3,0)--(0.5,0.4);
				\draw[-,ultra thick] (0.7,0)--(0.5,0.4);
				\draw[-,ultra thick] (0.5,0.4)--(0.5699596195707541,0.8417076540309386);

				\draw[dashed] (0.5,0.15)--(0.5,0.8);
				\draw[dashed] (0.7,0)--(0.7,0.25);

				\draw[->,ultra thick, red] (0.7,0)--(0.8,0) node[above]{$x$};
				\draw[->,ultra thick, red] (0.7,0)--(0.7,0.1) node[right]{$y$};

				\draw [->,thick,domain=-90:-116.5650512] plot ({0.5+0.15*cos(\x)}, {0.4+0.15*sin(\x)});
				\draw [->,thick,domain=90:116.5650512] plot ({0.7+0.15*cos(\x)}, {0.15*sin(\x)});
				\draw [->,thick,domain=90:81.00000000052139] plot ({0.5+0.3*cos(\x)}, {0.4+0.3*sin(\x)});

				\node at (0.4,0.2) [circle,fill,inner sep=1]{.};
				\node at (0.6,0.2) [circle,fill,inner sep=1]{.};
				\node at (0.5349798097853771,0.6208538270154693) [circle,fill,inner sep=1]{.};

				\node[text width=0mm] at (0.63,0.2) {$q_1$};
				\node[text width=0mm] at (0.43,0.2) {$q_2$};
				\node[text width=0mm] at (0.51,0.76) {$q_3$};

				\node[text width=0mm] at (0.55,0.16) {$m_1$};
				\node[text width=0mm] at (0.32,0.2) {$m_2$};
				\node[text width=0mm] at (0.56,0.62) {$m_3$};

				\node[text width=0mm] at (0.58,0.33) {$\dfrac{l_1}{2}$};
				\node[text width=0mm] at (0.38,0.33) {$\dfrac{l_2}{2}$};
				\node[text width=0mm] at (0.55,0.5) {$\dfrac{l_3}{2}$};
			\end{scope}
		\end{tikzpicture}
	\end{center}
	\caption{Representation of the three-link 2D biped model.}
	\label{fig::model}
\end{figure}

\newpage
